The design flaw of npm and how `everything' broke it

### 2024-02-27 Paper/2/Paper.tex
More rewording

\begin{abstract}
  npm (Node Package Manager) is a popular package manager owned by GitHub that
  allows developers to share node packages and libraries. This article will
  review and analyze the design flaw of npm and how it was broken by a single
  package, and will also review how GitHub responded to the incident and what
  actions they took in response.
\end{abstract}

@@

The npm registry is a critical piece of infrastructure for the entire JavaScript
community (and by extension, 99\% of websites \cite{w3techs}). Developers expect
that the npm registry would be reliable, secure, and complete. However, the
left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
incident in 2023 \cite{youtube-everything} have shown that the npm registry is
not as reliable as developers had hoped.

\section{Historical Background}
\subsection{Introduction}
One of the most infamous events in the history of npm was the left-pad incident.
Azer Koçulu is a software developer who was working on a personal project called
kik \cite{qz}. Coincidentally, Kik was also the name of a company in Ontario,
Canada \cite{qz, crunchbase}. The company reached out to Koçulu requesting that
he change the name of his project. Koçulu refused, and the company proceeded to
file a complaint with npm \cite{qz}. npm then decided to transfer the name kik
to the company, which caused Koçulu to remove all of his packages from the npm
registry, stating

@@

Unsurprisingly, npm also has a rate limit on how quickly packages can be
published \cite{npm-ratelimiting}. Thus, PatrickJS and Evan Boehs used a GitHub
Action workflow to publish the packages
\cite{youtube-everything,uncenter-blog-everything}.

>>>>

\begin{abstract}
  npm (Node Package Manager) is a popular package manager owned by GitHub that
  allows developers to share node packages and libraries \cite{npm}. This article will
  review and analyze the design flaw of npm and how it was broken by a single
  package, and will also review how GitHub responded to the incident and what
  actions they took in response.
\end{abstract}

@@

The npm registry is a critical piece of infrastructure for the entire JavaScript
community (and by extension, 99\% of websites \cite{w3techs}). Developers expect
that the npm registry will be reliable, secure, and complete. However, the
left-pad incident in 2016 \cite{npmblog-leftpad} and the everything package
incident in 2023 \cite{youtube-everything} have shown that the npm registry is
not as mature as developers had hoped.

\section{Historical Background}
\subsection{Introduction}
One of the most infamous events in the history of npm was the left-pad incident.
Azer Koçulu is a software developer who was working on a personal project called
kik \cite{qz}. Coincidentally, Kik was also the name of a company in Ontario,
Canada \cite{qz, crunchbase}. The company reached out to Koçulu requesting that
he change the name of his project. Koçulu refused, and the company proceeded to
file a complaint with npm \cite{qz}. npm (following its Dispute Resolutinon
Policy \cite{npm-dispute-policy}) then decided to transfer the name kik to the
company, which caused Koçulu to remove all of his packages from the npm
registry, stating

@@

Unsurprisingly, npm also has a rate limit on how quickly packages can be
published \cite{npm-ratelimiting,github-npm-ratelimiting}. Thus, PatrickJS and
Evan Boehs used a GitHub Action workflow to publish the packages
\cite{youtube-everything,uncenter-blog-everything}.
